% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Ben Ye}

\basicInfo{
  \email{yb532204897@gmail.com} \textperiodcentered\ 
  \phone{(+1) 857-204-6399} \textperiodcentered\
  \github[yeya24]{https://github.com/yeya24} \textperiodcentered\
  \linkedin[benye]{https://www.linkedin.com/in/ben-ye-9592b6158/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Northeastern University}, Boston, MA}{Sep. 2019 -- May. 2021}
\textit{Master in Computer Science}, GPA 4.0
\datedsubsection{\textbf{Wenzhou University}, China}{Sep. 2015 -- June. 2019}
\textit{B.S.} in Network Engineering, GPA 3.5

\section{\faUsers\ Experience}
\datedsubsection{RedHat, \textbf{SRE Intern}, Boston, MA}{May. 2020 -- Present}
\begin{itemize}
  \item Developed a Query Frontend component for \textbf{Thanos} to support better query planning and results caching.
  \item Created a cli for \textbf{AWS}, \textbf{GCP} and \textbf{OpenShift} to help SREs troubleshoot issues in different platforms.
\end{itemize}

\datedsubsection{PingCAP, \textbf{SWE Intern}, Remote}{Feb. 2020 -- May. 2020}
\begin{itemize}
  \item Designed and implemented a chaos testing framework based on \textbf{Kubernetes}, \textbf{Argo}, Loki and Chaos Mesh. 
  \item Optimized the data preparation time to 10x faster by adding multi-threaded CSV output support in to \textbf{go-tpc}.
  \item Managed a chaos testing platform in \textbf{EKS} \& \textbf{GKE} and monitored them using \textbf{Prometheus} stack and Loki.
  \item Developed a Grafana datasource plugin using \textbf{React} and \textbf{TypeScript} to visualize events of chaos testing.
\end{itemize}

\datedsubsection{Alibaba, \textbf{SWE Intern}, Hangzhou, China}{Jun. 2019 -- Sep. 2019}
\begin{itemize}
  \item Added Prometheus metrics, Grafana dashboard and Helm chart to \textbf{Dragonfly} project.
  \item Designed and implemented HA support to \textbf{Dragonfly} based on \textbf{gossip} algorithm. 
\end{itemize}

\datedsubsection{DaoCloud.io, \textbf{SWE Intern}, Shanghai, China}{Aug. 2018 -- May. 2019}
\begin{itemize}
  \item Developed a monitoring platform featured with management of clusters, targets, dashboards and alerts.
  \item Implemented a proxy for InfluxDB clusters to ensure data consistency using \textbf{Go} and \textbf{Redis}.
  \item Integrated platform alerting with SMS systems such as Dingtalk, WeChat and internal SNMP platfrom.
\end{itemize}

\section{\faKey\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Go, Java, Python, TypeScript, C
  \item Applications/Framework: Kubernetes, Docker, AWS, GCP, Prometheus, Grafana, Jenkins, MySQL, Jaeger
\end{itemize}

\section{\faCogs\ Personal Projects}
\datedsubsection{Promlinter}{July. 2020}
\begin{itemize}
  \item A \textbf{Go} static analysis linter for checking \textbf{Prometheus} metrics naming convention in Go code.
\end{itemize}

\datedsubsection{Machine Learning Collaboration Platform}{Mar. 2019 -- May. 2019}
\begin{itemize}
  \item Designed and implemented a ML platform featured with distributed training, gang-scheduling, dataset management and model serving based on \textbf{Kubeflow}.
  \item Implemented RESTful APIs for monitoring the resource usage(CPU, memory and GPU) of each training job.
\end{itemize}

\section{\faInfo\ Open Source Contribution}
\begin{itemize}[parsep=0.5ex]
  \item Maintainer of Kubeflow, Chaos Mesh, Dragonfly.
  \item Triage Team member of Thanos.
  \item Contributors of Kubernetes, Prometheus, Cortex, Loki, Prometheus Operator,etc.
  \item Speaker at KubeCon 2019 North America.
\end{itemize}

\end{document}
